Evolution of pre-copulatory and post-copulatory inbreeding behaviour

### 2016-10-27 pre_post_biorxiv.tex
Tweak margin inward

\begin{table}[!ht]
\captionsetup{margin={-1.75in,0.1in}}
\begin{adjustwidth}{-1.75in}{0in}
%\centering
\caption{\color{Gray}Individual traits (A), model parameter values (B), and model variables (C) for an individual based model of the evolution of polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy.}
\begin{tabular}{lllll}
\hline
A & Trait & Allele & Genotype & Phenotype &
\hline
  & Tendency for polyandry               &   $P_{a}$  &  $P_{g}$  &  $P_{p}$  &
  & Pre-copulatory inbreeding strategy   &   $M_{a}$  &  $M_{g}$  &  $M_{p}$  &
  & Post-copulatory inbreeding strategy  &   $F_{a}$  &  $F_{g}$  &  $F_{p}$  &
  &                                      &            &           &           &
\hline
B & Description & Parameter & & Default value(s) &
\hline

@@

 {\color{Gray}
\begin{adjustwidth}{-2.5in}{0in}
\mysidecaption{0.68}
{%
   \includegraphics[height=18cm]{figures/poly_costs.pdf}%
}%
{%
   \captionof{figures/poly_costs.pdf}\begin{justify}\vspace{10 mm} \textbf{Figure 1:} Mean allele values underlying tendency for polyandry (red lines and shading), pre-copulatory inbreeding strategy (i.e., blue lines and shading), and post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression. Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard errors of allele values around grand means. Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry. Panels in the left-hand column show simulations in which post-copulatory inbreeding strategy is fixed for random fertilisation (indicated by the black horizontal line), while panels in the right-hand column show evolution of both pre- and post-copulatory inbreeding avoidance. Costs of polyandry increase with rows from top to bottom. Dotted horizontal black lines in panels show values of zero on the y-axis.\end{justify}{\t}%
}[t]
\end{adjustwidth}
}

@@

{\color{Gray}
\begin{adjustwidth}{-2.5in}{0in}
\mysidecaption{0.68}
{%
   \includegraphics[height=10.25cm]{figures/Pp_vals.pdf}%
}%
{%
   \captionof{figures/poly_costs.pdf}\begin{justify}\vspace{0.25 mm} \textbf{Figure 2:} Relationship between polyandry allele values and phenotypes for an individual-based model in which pre- and post-copulatory inbreeding strategies evolve jointly with polyandry. Two simulations with identical starting conditions (default parameter values with no costs) are shown in panels A,B and C,D. Red lines in (A) and (C) show mean value of alleles underlying polyandry for a single replicate simulation over 40000 generations. Positive allele values contribute to polyandry, while negative values contribute to monandry (dotted line shows zero on the y-axis). In the last generation, mean allele value was below (A) or above (C) zero. Nevertheless, due to among-individual variation and the threshold nature of the polyandry phenotype, polyandry persists in the population in (A) and monandry persists in (C). The histograms in (B) and (D) show females' tendency for polyandry phenotypes in the last generation; white and grey shading indicates monandrous and polyandrous females, respectively.\end{justify}{\t}%
}[t]
\end{adjustwidth}
}

@@

{\color{Gray}
\begin{adjustwidth}{-2.5in}{0in}
\mysidecaption{0.31}
{%
   \captionof{figures/poly_costs.pdf}\begin{justify}\vspace{0.25 mm} \textbf{Figure 3:} Mean allele values underlying tendency for polyandry (red lines and shading), pre-copulatory inbreeding strategy (i.e., blue lines and shading), and post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression. Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard errors of allele values around grand means. Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry. Panel (A) shows evolution of costly pre-copulatory inbreeding strategy when post-copulatory inbreeding strategy is fixed for random fertilisation (solid black horizontal line), while (B) instead allows post-copulatory inbreeding strategy to evolve under otherwise identical conditions. Similarly, panel (C) shows evolution of costly post-copulatory inbreeding strategy when pre-copulatory inbreeding strategy is fixed for random mating (solid blue horizontal line), while (D) allows pre-copulatory inbreeding strategy to evolve under otherwise identical conditions.\end{justify}{\t}%
}
{%
   \includegraphics[height=14.5cm]{figures/rel_costs.pdf}%
}%
[t]
\end{adjustwidth}
}

@@

{\color{Gray}
\begin{adjustwidth}{-2.5in}{0in}
\mysidecaption{0.68}
{%
   \includegraphics[height=14cm]{figures/rel_costs.pdf}%
}%
{%
   \captionof{figures/fixed_adapt.pdf}\begin{justify}\vspace{0.25 mm} \textbf{Figure 4:} Mean allele values underlying tendency for polyandry (red lines and shading), pre-copulatory inbreeding strategy (i.e., blue lines and shading), and post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression. Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard errors of allele values around grand means. Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry. Panel (A) shows evolution of pre-copulatory inbreeding strategy given fixed polyandry (solid red line) and inbreeding avoidance (solid black line), and (B) shows these same conditions given a cost of pre-copulatory inbreeding strategy. Similarly, panel (C) shows evolution of polyandry and post-copulatory inbreeding strategy when pre-copulatory inbreeding strategy is fixed for inbreeding avoidance (solid blue line), while (D) shows these same conditions given a cost of post-copulatory inbreeding strategy.\end{justify}{\t}%
}[t]
\end{adjustwidth}
}

>>>>

\begin{table}[!ht]
\captionsetup{margin={-1.75in,0.1in}}
\begin{adjustwidth}{-1.75in}{0in}
%\centering
\caption{\color{Gray}Individual traits (A), model parameter values (B), and model variables (C) for an individual-based model of the evolution of polyandry, pre-copulatory inbreeding strategy, and post-copulatory inbreeding strategy.}
\begin{tabular}{lllll}
\hline
A & Trait & Allele & Genotype & Phenotype &
\hline
  & Tendency for polyandry               &   $P_{a}$  &  $P_{g}$  &  $P_{p}$  &
  & Pre-copulatory inbreeding strategy   &   $M_{a}$  &  $M_{g}$  &  $M_{p}$  &
  & Post-copulatory inbreeding strategy  &   $F_{a}$  &  $F_{g}$  &  $F_{p}$  &
  &                                      &            &           &           &
\hline
B & Description & Parameter & & Default value(s) &
\hline

@@

 {\color{Gray}
\begin{adjustwidth}{-2.2in}{0in}
\mysidecaption{0.68}
{%
   \includegraphics[height=18cm]{figures/poly_costs.pdf}%
}%
{%
   \captionof{figures/poly_costs.pdf}\begin{justify}\vspace{10 mm} \textbf{Figure 1:} Mean allele values underlying tendency for polyandry (red lines and shading), pre-copulatory inbreeding strategy (i.e., blue lines and shading), and post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression. Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard errors of allele values around grand means. Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry. Panels in the left-hand column show simulations in which post-copulatory inbreeding strategy is fixed for random fertilisation (indicated by the black horizontal line), while panels in the right-hand column show evolution of both pre- and post-copulatory inbreeding avoidance. Costs of polyandry increase with rows from top to bottom. Dotted horizontal black lines in panels show values of zero on the y-axis.\end{justify}{\t}%
}[t]
\end{adjustwidth}
}

@@

{\color{Gray}
\begin{adjustwidth}{-2.2in}{0in}
\mysidecaption{0.68}
{%
   \includegraphics[height=10.25cm]{figures/Pp_vals.pdf}%
}%
{%
   \captionof{figures/poly_costs.pdf}\begin{justify}\vspace{0.25 mm} \textbf{Figure 2:} Relationship between polyandry allele values and phenotypes for an individual-based model in which pre- and post-copulatory inbreeding strategies evolve jointly with polyandry. Two simulations with identical starting conditions (default parameter values with no costs) are shown in panels A,B and C,D. Red lines in (A) and (C) show mean value of alleles underlying polyandry for a single replicate simulation over 40000 generations. Positive allele values contribute to polyandry, while negative values contribute to monandry (dotted line shows zero on the y-axis). In the last generation, mean allele value was below (A) or above (C) zero. Nevertheless, due to among-individual variation and the threshold nature of the polyandry phenotype, polyandry persists in the population in (A) and monandry persists in (C). The histograms in (B) and (D) show females' tendency for polyandry phenotypes in the last generation; white and grey shading indicates monandrous and polyandrous females, respectively.\end{justify}{\t}%
}[t]
\end{adjustwidth}
}

@@

{\color{Gray}
\begin{adjustwidth}{-2.2in}{0in}
\mysidecaption{0.31}
{%
   \captionof{figures/poly_costs.pdf}\begin{justify}\vspace{0.25 mm} \textbf{Figure 3:} Mean allele values underlying tendency for polyandry (red lines and shading), pre-copulatory inbreeding strategy (i.e., blue lines and shading), and post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression. Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard errors of allele values around grand means. Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry. Panel (A) shows evolution of costly pre-copulatory inbreeding strategy when post-copulatory inbreeding strategy is fixed for random fertilisation (solid black horizontal line), while (B) instead allows post-copulatory inbreeding strategy to evolve under otherwise identical conditions. Similarly, panel (C) shows evolution of costly post-copulatory inbreeding strategy when pre-copulatory inbreeding strategy is fixed for random mating (solid blue horizontal line), while (D) allows pre-copulatory inbreeding strategy to evolve under otherwise identical conditions.\end{justify}{\t}%
}
{%
   \includegraphics[height=14.5cm]{figures/rel_costs.pdf}%
}%
[t]
\end{adjustwidth}
}

@@

{\color{Gray}
\begin{adjustwidth}{-2.2in}{0in}
\mysidecaption{0.68}
{%
   \includegraphics[height=14cm]{figures/rel_costs.pdf}%
}%
{%
   \captionof{figures/fixed_adapt.pdf}\begin{justify}\vspace{0.25 mm} \textbf{Figure 4:} Mean allele values underlying tendency for polyandry (red lines and shading), pre-copulatory inbreeding strategy (i.e., blue lines and shading), and post-copulatory inbreeding strategy (i.e., black lines and shading), as calculated across all individuals within a population over 40000 generations given strong inbreeding depression. Solid lines represent grand means over 40 replicate populations, and shading around solid lines show standard errors of allele values around grand means. Negative mean allele values reflect strategies of inbreeding avoidance or tendency for monandry, and positive values reflect strategies of inbreeding preference or tendency for polyandry. Panel (A) shows evolution of pre-copulatory inbreeding strategy given fixed polyandry (solid red line) and inbreeding avoidance (solid black line), and (B) shows these same conditions given a cost of pre-copulatory inbreeding strategy. Similarly, panel (C) shows evolution of polyandry and post-copulatory inbreeding strategy when pre-copulatory inbreeding strategy is fixed for inbreeding avoidance (solid blue line), while (D) shows these same conditions given a cost of post-copulatory inbreeding strategy.\end{justify}{\t}%
}[t]
\end{adjustwidth}
}
